Predicting Tags for StackOverflow Posts

### 2013-03-03 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 069494f48b98c0cff6aeeb40d494a48656b3fe73 [formerly 319a1a8924d8dc79d32072444964c0d7197e7332]
Former-commit-id: afd8f2b8763025de1c3cd5eba0e30dc28c7f0f46

\begin{abstract}
  Large-scale rich behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study trends of human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian probabilistic model that can predict the hashtags used by the author of the post.
  Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
  so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of hundreds of millions of chunks occur in less than one second on a single processor.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.

@@

\citeA{Bird2009} recommended to remove the low-predictor stop words from the analysis.
\citeauthor{Bird2009} provided a short list that were commonly removed (e.g., ``the'', ``and'', ``or'').
However it seemed somewhat arbitrary to remove an explicitly-enumerated list of stop words.
Looking at the scaled entropy measure, it seems quite plausible that this measure of word predictiveness can also be used to identify stop words.
That is, words with scaled entropy close to zero are the stop words.
Looking at the lowest ten scaled-entropy words for this dataset, (``does'', ``anyone'', ``'ve'', ``found'', ``are'', ``seems'', ``has'', ``been'', ``for'', ``support''),
using scaled entropy to determine stop words works fairly well.
So instead of explicitly removing an enumerated list of stop words, we used a data-driven approach and let the scaled entropy measure attenuate the words that were not predictive of any tag to near-zero levels.

>>>>

\begin{abstract}
  Large-scale behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study trends of human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian probabilistic model that can predict the hashtags used by the author of the post.
  Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
  so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of hundreds of millions of chunks occur in less than one second on a single processor.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.

@@

\citeA{Bird2009} recommended to remove the low-predictor stop words from the analysis.
\citeauthor{Bird2009} provided a short list that were commonly removed (e.g., ``the'', ``and'', ``or'').
However it seemed somewhat arbitrary to remove an explicitly-enumerated list of stop words.
Looking at the scaled entropy measure, it seems quite plausible that this measure of word predictiveness can also be used to identify stop words.
That is, words with scaled entropy close to zero \emph{are} the stop words.
Looking at the lowest ten scaled-entropy words for this dataset, (``does'', ``anyone'', ``'ve'', ``found'', ``are'', ``seems'', ``has'', ``been'', ``for'', ``support''),
using scaled entropy to determine stop words works fairly well.
So instead of explicitly removing an enumerated list of stop words, we used a data-driven approach and let the scaled entropy measure attenuate the words that were not predictive of any tag to near-zero levels.
